---
title: "R Notebook"
output: html_notebook
---

#Loading packages

```{r}
library(tidyverse)
library(vegan)

```

#Getting the common name for all 120 species, with habitat (rainforest/open-country) and habit (canopy, mid-storey, ground, understorey, aquatic, aerial)
```{r}
species_names <- read.csv("data/species-trait-dat.csv") %>%
  rename ("Species" = common_name)
```

#Preparing point-count data, with abundance data (0 to n) for 69 sites arosss visits, to use for an NMDS plot. Wide data.
```{r}
# load list of sites
sites <- read.csv("data/list-of-sites-acoustic-study.csv") %>%
  filter(Site.code != "OLCAP5B")

# read point count data
pointcount_data <- read.csv("data/filt_data.csv") %>%
  select (Site_ID, Site_type, Species, Date, Number) %>%
  mutate (Site_ID = str_replace_all (Site_ID, "_", "")) %>%
  mutate (Site_type = str_replace_all (Site_type, "Restored", "AR")) %>%
  mutate (Site_type = str_replace_all (Site_type, "Unrestored", "NR")) %>%
  mutate (Site_type = str_replace_all (Site_type, "Benchmark", "BM")) %>%
  rename ("Treatment" = Site_type) %>%
  add_column (Method = "pc") %>%
  mutate(forRichness = case_when(Number>0 ~ 1,Number==0 ~ 0)) %>%
  select(Site_ID, Species, forRichness) %>%
  group_by(Site_ID, Species) %>%
  mutate(abundance = sum(forRichness)) %>%
  select(-forRichness) %>%
  distinct(.)

# filter to include only sites sampled in Ramesh et al.
pointcount_data <- merge(pointcount_data, sites, by.x = "Site_ID", by.y = "Site.code")
pointcount_data <- pointcount_data[,1:5]



%>% 
  summarise (Number=sum(Number)) %>% 
  arrange(Treatment) #%>%
  #pivot_wider (names_from = Species, values_from = Number, values_fill = list(Number=0))


```

#Preparing annotated acoustic data, with detection data (from 0 to n) for 43 sites, to use for an NMDS plot. Wide data.
```{r}
acoustic_data <- read.csv ("data/vocal-detections-data.csv") %>%
  group_by(Site, Restoration.type, Date) %>%
  transform() %>% replace(is.na(.), 0) %>%
  summarise_at(.vars = vars(c("IP":"HSWP")),.funs = sum) %>%
  pivot_longer(cols=IP:HSWP, names_to = "Species", values_to = "vocalDetections") %>%
  rename ("Site_ID" = Site, "Site_type" = Restoration.type, "species_annotation_codes" = Species) %>%
  replace(is.na(.), 0) %>%
  left_join(species_names) %>%
  mutate (Site_type = str_replace_all (Site_type, "Active", "AR")) %>%
  mutate (Site_type = str_replace_all (Site_type, "Passive", "NR")) %>%
  mutate (Site_type = str_replace_all (Site_type, "Benchmark", "BM")) %>%
  rename ("Treatment" = Site_type, "Number" = vocalDetections) %>%
  add_column (Method = "ac") %>%
  mutate(forRichness = case_when(Number>0 ~ 1,Number==0 ~ 0)) %>%
  select(Site_ID, Species, forRichness) %>%
  group_by(Site_ID, Species) %>%
  mutate(abundance = sum(forRichness)) %>%
  select(-forRichness) %>%
  distinct(.)
```

# Adding the two dataframes together, with 0s in the point count data for absent species
```{r}

```


#Converting the dataframes to matrices to make an NMDS plot
```{r}
pointcount_data <- as.matrix (pointcount_data [, 3:ncol(pointcount_data)])
acoustic_data <- as.matrix (acoustic_data [, 3:ncol(acoustic_data)])

```
